Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-10 thirdPaper/draft/typeConeAssociahedra.tex
Changed order: Coro 4.43 is now Coro 4.46.

The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b g$-vectors.

\begin{proposition}
\label{prop::exchange conflations are unique}
 Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.  Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.  Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ are two mutation conflations (see Definition~\ref{defn::mutation conflation}.  
 Then~$E$ and~$E'$ are isomorphic. \pg{Is is possible that~$X$ and~$Y$ are permuted in one of the exchange conflations?}
\end{proposition}
\begin{proof}
 By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.  The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{prop::2kbproj-is-extriangulated}).  In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.  Thus~$E$ and~$E'$ are isomorphic.
\end{proof}

% Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
Before stating our next theorem, we first recall some definitions

@@

>>>>

The extriangulated category~$K^{[-1,0]}(\proj \Lambda)$ is the setting in which we can finally prove point~(ii) of Proposition~\ref{prop:exchangeablePairsNKC}, using results of~\cite{DemonetIyamaJasso} on~$\b g$-vectors.  
% Proposition~\ref{prop::2kbproj-is-extriangulated} gives a setting in which to apply Theorem~\ref{}.
Before doind so, we introduce the notion of mutation conflation for two-term silting objects.

@@

\begin{proposition}
\label{prop::exchange conflations are unique}
 Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field.  Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$.  Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ (or~$Y\infl E'\defl X$) are two mutation conflations (see Definition~\ref{defn::mutation conflation}.  
 Then~$E$ and~$E'$ are isomorphic. \pg{Is it possible that~$X$ and~$Y$ are permuted in one of the exchange conflations?}
\end{proposition}
\begin{proof}
 By~\cite[Theorem 6.5]{DemonetIyamaJasso} (based on~\cite[Theorem 2.3]{DehyKeller}), rigid objects in~$K^{[-1,0]}(\proj \Lambda)$ are determined by their~$\b g$-vector.  The datum of the~$\b g$-vector of an object of~$K^{[-1,0]}(\proj \Lambda)$ is equivalent to that of its class in the Grothendieck group~$K_0(K^{[-1,0]}(\proj \Lambda))$, where~$K^{[-1,0]}(\proj \Lambda)$ is viewed as an extriangulated category (see Proposition~\ref{prop::2kbproj-is-extriangulated}).  In this Grothendieck group, we have that~$[E] = [E'] = [X]+[Y]$.  Thus~$E$ and~$E'$ are isomorphic.
\end{proof}

We now come to the main result of this section.
